Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-02-16 Paper.tex
Footnote clarifying Ethereum 1.0 and link to wiki FAQs on PoS & sharding

One plague of the Bitcoin world is ASICs. These are specialised pieces of compute hardware that exist only to do a single task (\cite{ASICSmithMJS}). In Bitcoin's case the task is the SHA256 hash function (\cite{Courtois2014}). While ASICs exist for a proof-of-work function, both goals are placed in jeopardy. Because of this, a proof-of-work function that is ASIC-resistant (i.e. difficult or economically inefficient to implement in specialised compute hardware) has been identified as the proverbial silver bullet.

Two directions exist for ASIC resistance; firstly make it sequential memory-hard, i.e. engineer the function such that the determination of the nonce requires a lot of memory and bandwidth such that the memory cannot be used in parallel to discover multiple nonces simultaneously. The second is to make the type of computation it would need to do general-purpose; the meaning of ``specialised hardware''  for a general-purpose task set is, naturally, general purpose hardware and as such commodity desktop computers are likely to be pretty close to ``specialised hardware'' for the task. For Ethereum 1.0 we have chosen the first path.

>>>>

One plague of the Bitcoin world is ASICs. These are specialised pieces of compute hardware that exist only to do a single task. In Bitcoin's case the task is the SHA256 hash function. While ASICs exist for a proof-of-work function, both goals are placed in jeopardy. Because of this, a proof-of-work function that is ASIC-resistant (i.e. difficult or economically inefficient to implement in specialised compute hardware) has been identified as the proverbial silver bullet.

Two directions exist for ASIC resistance; firstly make it sequential memory-hard, i.e. engineer the function such that the determination of the nonce requires a lot of memory and bandwidth such that the memory cannot be used in parallel to discover multiple nonces simultaneously. The second is to make the type of computation it would need to do general-purpose; the meaning of ``specialised hardware''  for a general-purpose task set is, naturally, general purpose hardware and as such commodity desktop computers are likely to be pretty close to ``specialised hardware'' for the task. For Ethereum 1.0 we have chosen the first path.\footnote{Ethereum 1.0 uses proof-of-work, while it is planned that Ethereum 2.0 will include \href{https://github.com/ethereum/wiki/wiki/Proof-of-Stake-FAQ}{proof-of-stake} and \href{https://github.com/ethereum/wiki/wiki/Sharding-FAQ}{sharding}.}
